---
title: "Model Descriptions"
author: "Matt Weldy"
date: "3/9/2021"
bibliography: bibliography.json
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Huggins model

The conditional likelihood abundance estimator proposed by @huggins_statistical_1989 and @alho_logistic_1990, which was further extended in @huggins_practical_1991, is an extension to previous abundance estimators to account for heterogeneous capture probabilities ($p$). The model estimates individual capture probabilities and abundance conditional on captured individuals.

$$  \mathcal{L} = \prod_{i=1}^n \prod_{t=1}^t p_{i,t}^{z_{i,t}}(1-p_{i,t})^{1-z_{i,t}} $$
where, \linebreak
  $z_{i,t}$ takes the value of 1 if individual $i$ has been captured before occasion $t$ and 0 otherwise.

Thus the capture history $y_{i,t}$ is used to estimate the capture probability of individual $i$ as a Bernoulli trial,
$$y_{i,t} \sim Bernoulli(p_{i,t}) $$
and abundance $\hat{N}$ is derived condtional on the count of known individuals ($C$), sometimes referred to the minimum number of known alive ($MNKA$).
$$\hat{N} = \frac{C}{1-\prod^{t}(1-p_t)}$$
Variation in detection probability can be modeled using linear logistic models or other variations used to estimate probabilities 0-1.


```{r cars}
summary(cars)
```

## CJS model

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
